\input{sections/introduction}
%\clearpage
\input{sections/methods}
%\clearpage
\input{sections/formulation}
%\clearpage
\input{sections/optimization}
%\clearpage
\input{sections/results-discussion}
%\clearpage

\section{Conclusion}

% Summary:
\ifdefined\DISSERTATION
    This paper applies the MDOcean semi-analytical modeling framework \citet{mccabe_development_2026}, which spans WEC geometry, hydrodynamics, dynamics and control, structures, and economics, within a Multidisciplinary Design Optimization (MDO) approach to maximize power and minimize cost of the RM3 point absorber.
\else
    This paper applies the MDOcean semi-analytical modeling framework \citet{mccabe_development_2026} within a Multidisciplinary Design Optimization (MDO) approach to maximize power and minimize cost of the RM3 point absorber.
\fi

% Formulation
\ifdefined\DISSERTATION
    The optimization problem is formulated systematically, with numerical implications such as linearity, convergence, and feasibility in mind, around 12 design variables representing bulk dimensions, structural thicknesses, and powertrain ratings.
    All disciplines are optimized at once, overcoming the loss of system optimality inherent in sequential optimization of coupled disciplines.
    Constraints prevent numerical overflow and structural failure and ensure geometric physicality, pitch stability, positive buoyancy, sufficient ballast volume, positive power, and compliance with dynamic limits including powertrain ratings and amplitude restrictions.
    The gradient-based SQP algorithm leverages the problem's underlying smoothness to aid convergence, used both for single-objective optimization and to generate seeds for multi-objective optimization; after generating \resultsRE[numParetoSeeds]~seeds via the epsilon-constraint method, a gradient-free pattern search fills in the Pareto front for a total of \resultsRE[numParetoSearchPoints]~points.
\else
    The optimization is formulated systematically, with numerical linearity, convergence, and feasibility in mind, around 12 design variables spanning bulk dimensions, structural thicknesses, and powertrain ratings, with all disciplines optimized at once to overcome the loss of system optimality inherent in sequential optimization of coupled disciplines.
    Constraints prevent numerical overflow and structural failure and ensure geometric physicality, stability, buoyancy, ballast, positive power, and compliance with powertrain and amplitude limits.
    The gradient-based SQP algorithm aids convergence by exploiting the problem's smoothness, generating \resultsRE[numParetoSeeds]~seeds via the epsilon-constraint method that a gradient-free pattern search extends to \resultsRE[numParetoSearchPoints]~Pareto points.
\fi

% Results
Single-objective optimization to minimize LCOE yields a design with \resultsRE[pctImproveDesignCostMinLCOE]~lower design cost and \resultsRE[pctImprovePowerMinLCOE]~higher power, a \resultsRE[pctImproveLCOEMinLCOE]~improvement over the original RM3 design; these reach \resultsRE[pctImprovePowerMaxPower]~more power or \resultsRE[pctImproveDesignCostMinCapex]~less cost when optimizing for maximum power or minimum cost respectively.
\ifdefined\DISSERTATION
    The optimal designs have noticeably larger diameters and drafts, lower above-water spar profiles, thinner structural material, and powertrains similar in size to the nominal RM3.
    Due to the non-convex, highly constrained nature of the problem, a multistart with \resultsRE[numMultistartRequired]~random initial conditions is required for a 95\% chance of finding the presumed global optimum.
    Parameter sensitivities show LCOE is highly sensitive to wave characteristics, efficiency, and the fixed charge rate, while design cost is highly sensitive to bulk and structural damping plate dimensions, the price of PTO power, site parameters, and material choice.
    The optimal design variables are sensitive to wave characteristics, motivating site-specific designs, and to geometric parameters, suggesting the addition of $D_d$, $T_{f,1}$, $T_s$, and possibly $D_{f,in}$ as design variables in future work.
    A global sensitivity to deployment location across four U.S.\ sites reveals that incident wave power drives LCOE and that in Hawaii, where wave periods are shorter, the optimal design unexpectedly has a \resultsRE[HawaiiDesignCharacteristics]~than on the U.S.\ West Coast, where longer waves dominate.
    Finally, the sensitivity to modeling assumptions shows that allowing force saturation as a control strategy enables a \resultsRE[pctLCOEIncreaseForceSatOptMinLCOE]~reduction in LCOE relative to an optimal design without it, which is compelling evidence for developers to select a powertrain rated below the highest expected impedance-matched force.
\else
    The optimal designs have larger diameters and drafts, lower above-water spar profiles, and thinner structural material, with powertrains similar in size to the nominal RM3, and the non-convex, highly constrained problem requires a \resultsRE[numMultistartRequired]-point multistart for a 95\% chance of the presumed global optimum.
    Sensitivity analysis shows LCOE is most sensitive to wave characteristics, efficiency, and the fixed charge rate, and design cost to damping plate dimensions, PTO power price, site parameters, and material choice; the optimal design is sensitive to wave characteristics (motivating site-specific designs) and to geometric parameters $D_d$, $T_{f,1}$, $T_s$, and possibly $D_{f,in}$ (suggesting their promotion to design variables).
    A global sensitivity across four U.S.\ deployment sites shows incident wave power drives LCOE, with Hawaii's shorter wave periods yielding an optimal design with a \resultsRE[HawaiiDesignCharacteristics]~than on the West Coast.
    %, and that allowing force saturation enables a \resultsRE[pctLCOEIncreaseForceSatOptMinLCOE]~LCOE reduction relative to an optimal design without it --- compelling developers to rate the powertrain below the highest expected impedance-matched force.
\fi
% Meanwhile, control scheme, drag, and degrees of freeom \hl{results await analysis}.

\ifdefined\DISSERTATION
    After this analysis of the single-objective results, the trade-off between cost and power is examined using multi-objective optimization.
    The Pareto front contains a non-convex cusp: below \resultsRE[powerWhereCusp] average power, cost declines sharply for only small power decreases, corresponding to a strategy shift in which power saturation, rather than force saturation, becomes optimal at these lower powers.
    Lower powers also favor larger drafts, smaller float diameters, larger spar diameters, and thinner structures.
    A previously proposed concept of trading off power and cost across WEC use cases through the PTO alone, without modifying the hydrodynamic and structural design, is shown to be minimally effective, since most of the cost reduction at low power comes from reduced material cost rather than PTO cost.
    The multi-objective optimization runs in just \resultsRE[paretoRuntime]~on a 14-core server, a large improvement over the many hours required by previous WEC design optimization studies.
    Surprisingly, however, the use of gradients does not aid convergence enough to offset the additional function evaluations required for finite-difference derivatives, so constructing the Pareto front takes several times as many function evaluations as previous genetic-algorithm optimizations.
\else
    The cost-power trade-off is then examined via multi-objective optimization.
    The Pareto front contains a non-convex cusp: below \resultsRE[powerWhereCusp] average power, cost declines sharply for small power decreases, corresponding to a shift in which power saturation, rather than force saturation, becomes optimal at low power; lower powers also favor larger drafts, smaller float diameters, larger spar diameters, and thinner structures.
    A previously proposed concept of trading power for cost through the PTO alone, leaving the hydrodynamic and structural design fixed, is shown to be minimally effective, since most low-power cost reduction comes from material rather than PTO savings.
    The optimization runs in just \resultsRE[paretoRuntime]~on a 14-core server, which is far faster than the hours required by prior studies, though, surprisingly, gradients do not aid convergence enough to offset the finite-difference evaluation cost, so the Pareto front takes several times as many function evaluations as prior genetic-algorithm optimizations.
\fi

% Discussion
\ifdefined\DISSERTATION
    A key feature of this study that other WEC optimizations lack is the modeling of more realistic effects such as shape-informed structural stress, force saturation, amplitude limits, and a nonlinear drag model.
    Nonetheless, the structural loads and stresses carry high uncertainty, the effects of PTO dynamics and irregular waves are omitted, and only a single WEC type (two-body axisymmetric point absorber) is considered.
    Future modeling work should address these limitations, and the next iteration should enhance the formulation by adding design variables such as PTO components and geometric ratios, along with requirements for mooring loads, structural resonance, installation, manufacturing, reliability, and regulatory compliance.
    Finally, analysis extensions such as a global sensitivity sweep assessing combined deviations in parameter inputs and model assumptions would enable a more thorough evaluation of the optimal design's robustness and the design-space trade-off between optimality and robustness.
\else
    A key feature this study adds over other WEC optimizations is the modeling of realistic effects, such as shape-informed structural stress, force saturation, amplitude limits, and nonlinear drag, though structural loads remain uncertain, PTO dynamics and irregular waves are omitted, and only a two-body axisymmetric point absorber is considered.
    Future work should address these modeling limitations, enhance the formulation with additional design variables (PTO components, geometric ratios) and requirements (mooring, structural resonance, installation, manufacturing, reliability, regulatory compliance), and add global sensitivity sweeps over combined parameter and model-assumption uncertainty to assess robustness.
\fi

% Impact of findings:
The results of this study inform future WEC design optimization, highlighting the complex trade-off between power and cost, the necessity of accounting for multidisciplinary coupling, and the value of employing clever simulation and optimization techniques to reduce runtime and facilitate convergence.
