% \emph{The people you love will change you.
% The things you have learned will guide you. 
% And nothing on earth can silence the quiet voice still inside you.} 

% - Moana

The PhD was hard in a way that undergrad wasn't.
The technical challenges were simple compared to the emotional, mental, and institutional challenges.
I learned a lot about myself and what I need to be successful,
how to navigate inaccessible systems, how to advocate for myself and others, 
and how to both enact and know the limits of grassroots systemic change.
I got a lot of experience building, overhauling, 
and refining the processes and systems that help me navigate these challenges.
I am grateful to everyone who supported me through the process,
as well as for those in my early life who helped me gain the qualifications necessary to start a PhD program to begin with.

First, I thank my academic and professional mentors and supporters, including:
\begin{itemize}
  \item Maha for taking me on as a student and ultimately persisting with me through the PhD process
  \item My committee members, Jacob Mays, Pat Reed, and Ryan Coe, for their technical insight and feedback
  \item Sam Benson and Dmitry Savransky, for stepping in to provide additional departmental advising support when I needed it 
  \item NREL for my undergraduate internship which exposed me to marine energy, includng my menor Scott Jenne
  \item Andras Kiss, my mentor at my internship at Infinite Cooling, 
  for showing me what someone with a PhD can do in industry and for being my role model
  \item Racecar (the MIT Formula SAE Team) for raising me as an engineer, giving me the technical skills 
  in multidisciplinary modeling, and providing practical experience on a design team
  \item Laila Nashid, tutor through the Cornell Graduate Writing Service, for practical advice on strengthening my written argument
  \item My physical and mental healthcare support and advising system, 
  including Rachel Clark, Dawn Plue, Erin Forquer, Ila Rose, and Matt Jarman.
\end{itemize}

Next, I thank my academic and extracurricular peers at Cornell:
\begin{itemize}
  \item SEA Lab for being a fun and supportive research group: 
  Can Jam on the fifth floor of Upson, PhD meetings, running, and the hot tub
  \item Olivia V. for being my best friend in the lab, conference buddy, 
  and for being there for each other when our PhDs were hard
  \item Nate, Matt, and Kapil, for making the lab fun with their antics and icebreakers. 
  One day we'll build a nuclear outer-space WEC.
  \item Other MAE PhD students, including Colby, Charlotte, Diane, Jared. 
  The DnD campaign where Onaam Timunuo got to meet his grandfather, who talks to rocks, was a highlight for sure.
  \item Everyone who was willing to body double with me while writing this dissertation, including 
  Colby, Arthur, Joe, Demola, Stefan, Matt, Olivia V., Olivia G., Shariwa, Sam, Hana, Jared, and Yuxin.
  \item All the undergrads I've had the pleasure of mentoring, 
  including Madison who has worked with me for 4 years and has grown so much, 
  Bimali who went above and beyond on the MEEM project,
  and En, Andrea, and Moho, who turned Wait Terrace into a SEA Lab house.
  Teamwork is really important to me, and working with you all has been a highlight of my PhD.
  \item Flor for being a devoted SNAC advisor; and SNAC members 
  including Matthew, Anthony, Jessa, Will, Ethan, Sierra, and Aishat
  \item The engineering leadership program, including professor Rob Parker and Erica Dawson, 
  the Geckos cohort, and the GAIA co-founders Mark Tarazi and Mohamed Aden.
  \item other GAIA members, including AJ, Nicholas, Sofia, Erick
\end{itemize}

Next, I thank my friends and housemates outside of the academic environment, including:
\begin{itemize}
  \item Meghana for being the best friend I could ask for and always being a phone call away 
  for life debriefs, support, and even the times where 
  we just exist together mutually distracted on the phone.
  You have been my sounding board and an invaluable friend for
  every part of the grad school experience,
  from deciding what university to attend to finishing my dissertation.
  Thanks for calling me out on my perfectionism, 
  helping me reflect on what I've learned about myself and what I want, 
  and for just getting me.
  You sometimes know me better than I know myself, 
  and I would be a different person without you.
  \item Meghana, Alex, Sandy, and Nathan, for letting me crash at their apartments
  during my frequent visits to Boston; driving all the way to Ithaca to see my defense;
  and providing moral support and more during the final stretch.
  \item the CGSU graduate union for their energy to stand up to injustices 
  that are startlingly common in academia and beyond,
  and willingness to fight for me and my fellow graduate students
  \item the wonderful housemates of Wait Terrace cooperative 
  for late night wagon rides, floor time, squirrels in the walls, fridge quotes, and karaoke
  \item Marina, Karen, and Marc, for cultivating a thriving house culture 
  full of Bob the Builder cakes, eight foot inflatable gnomes, and British accents.
  \item Ilana, Olivia G., and Firdavs, for being great co-house managers 
  and spending lovely midnights together on the Beebe Lake bridge. 
  I leave the house in your capable hands.
  \item Andrea, my former roommate, for the spontaneous runs, deep reflections, and meaningful conversations about impact
  \item Olivia G., another housemate who has been there for me through the end,
  and whose knack for research and writing helped me see my project in a new light 
  \item Ilana, my beloved roommate for the last 1.5 years, 
  who has been there for both the uncontrollable giggles and the uncontrollable tears.
  Yes, you can still be my roommate even if you turn into Kafka's beetle, 
  a pickled worm in a jar, or an inanimate object.
  Thanks for encouraging me to write Sun articles, 
  inviting me on that barefoot 4am walk to Goldwin Smith, 
  and helping me cement my identity.
  You're like a little sister to me, and I can't wait to see what's ahead for you.
\end{itemize}

Finally, I thank my family, including:
\begin{itemize}
  \item Brielle, who really is a little sister to me, 
  for sending me encouragement, hometown updates, handmade craft gifts, 
  and hidden little notes that always make me smile;
  and for creating the wave image used in this dissertation.
  \item My parents, for raising me to love learning enough to start a PhD 
  and to have the persistence to finish it.
  You keep a watchful eye on the Cornell red-tailed hawk cam, 
  and the annual excitement of the fledging of the hawks has marked the milestones of my PhD journey.
  I hope that with this dissertation, I have likewise taken flight.
  My mom braved \LaTeX as a complete beginner to help proofread my dissertation materials,
  and my dad helped keep me motivated in the final semester with captivating photos of the National Parks.
\end{itemize}


To everyone who has supported and encouraged me throughout this journey, thank you.
I love you all.