\documentclass[phd,tocprelim]{cornell}
%
% tocprelim option must be included to put the roman numeral pages in the
% table of contents
%
% The cornellheadings option will make headings completely consistent with
% guidelines.
%
% This sample document was originally provided by Blake Jacquot, and
% fixed up by Andrew Myers.
%
% Shared packages
\usepackage{import}
\subimport{../shared}{shared-pkg}
\subimport{../applied-ocean-research-model}{commands-aor}
\subimport{../renewable-energy-mdo}{commands-re}

% From template
\usepackage{graphicx,pstricks}
\usepackage{graphics}
\usepackage{moreverb}
%\usepackage{subfigure}
\usepackage{epsfig}
\usepackage{hangcaption}
\usepackage{txfonts}
\usepackage{palatino}

% For bibliography
\usepackage{natbib}

% for grid paper
\usepackage{framed}
\usepackage{adjustbox}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage[svgnames]{xcolor}
\usepackage{titlesec}
\usepackage{wrapfig}
\usepackage{caption}

% for subtitles
\usepackage{titlesec}

\makeatletter
\titleformat{\chapter}[display]
{\normalfont\bfseries}{\Large\centering\MakeUppercase{\@chapapp\space \thechapter}}{0pt}{\LARGE\center}
\titlespacing*{\chapter}{0pt}{-20pt}{20pt}

\graphicspath{
  {../../mdocean/simulation/modules/OpenFLASH/pubs/JFM/}
  {../applied-ocean-research-model/}
  {../renewable-energy-mdo/}
}

% adjust margins
\usepackage[
  top=1in,
  bottom=1in,
  left=1in,
  right=1in
]{geometry}

%if you're having problems with overfull boxes, you may need to increase
%the tolerance to 9999
\tolerance=9999

\bibliographystyle{plainnat}
%\bibliographystyle{IEEEbib}

\newcommand{\DISSERTATION}{} % used for dissertation-specific formatting in shared files

\renewcommand{\caption}[1]{\singlespacing\hangcaption{#1}\normalspacing}
\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}
\renewcommand{\floatpagefraction}{0.75}

\title {Leveraging Semi-Analytical Modeling, Multidisciplinary Design Optimization, 
        and System Value Metrics to Advance Wave Energy Converter Viability}
\author {Rebecca McCabe}
\conferraldate {August}{2026}
\degreefield {Ph.D.}
\copyrightholder{Rebecca McCabe}
\copyrightyear{2026}

\begin{document}

\maketitle
\makecopyright

\begin{abstract}
Wave energy converters (WECs) can advance the global energy transition by harnessing ocean waves to produce clean power for utility grids and offshore activities.
This dissertation describes (1) the development of a fast and accurate computational model to simulate the WEC including hydrodynamics, constrained optimal control, and structural survival;
(2) the application of the model in a systems optimization framework to understand how WEC shape and size mediate the tradeoff between cost and power;
and (3) the extension of this framework to holistically incorporate techno-economic viability and environmental impacts at the grid level.

Guided by a first-principles understanding of frequency-domain dynamics and a geometric interpretation of the constrained optimal control problem, we quasi-linearize the drag and force saturation nonlinearities and solve the resulting low-order quadratic program analytically.
The simplified dynamics model achieves runtimes 10-1000x faster than prior state-of-the-art with acceptable accuracy (errors of 1-10\%).
We combine this quasi-linearized dynamics model with mathematical models for concentric-cylinder hydrodynamics, stiffened-plate structural stress, hydrostatic stability, allowable oscillation amplitude, and material and component cost to form a multidisciplinary WEC simulation.
We release the software and corresponding numerical benchmarks open source as MDOcean and OpenFLASH.

The subsequent design study leverages the model's efficiency and structure to enable a more comprehensive and thoughtful search of the design space.
We synthesize aspects of multidisciplinary design optimization, control co-design, techno-economic analysis, and systems engineering to create an integrated methodology for WEC design optimization that incorporates necessary coupling while remaining computationally efficient and robust to uncertainty.
We demonstrate ~50\% reduction in the levelized cost of energy, outline the dominant role of powertrain constraints in the power-cost balance, derive sensitivities, and discuss implications for WEC design and future model development.
Finally, we revise the framework by integrating life cycle analysis and capacity expansion modeling to maximize more meaningful net value metrics including profitability and avoided carbon emissions.
Preliminary results suggest that while seasonal grid variation complicates the power-cost tradeoff, carbon emissions can be considered more simply.
The system design process articulated here can generalize to other emerging energy technologies, ultimately advancing the decarbonization of the electricity sector.
\end{abstract}

% todo: plain language abstract

\begin{biosketch}
Becca is a 5th-year Ph.D. candidate in Mechanical Engineering interested in the design of renewable energy systems.
She enjoys solving integrated mechanical, electromagnetic, fluid, and controls problems through simulation, systems design, and prototyping.
Her PhD research at Cornell's Symbiotic Engineering and Analysis Lab with Prof. Maha Haji involves 
optimizing ocean wave energy toward economic viability and reduced carbon emissions. 
Outside of research, Becca enjoys distance running, working with engineering for social impact organizations, and neurodiversity advocacy.
During her PhD, she completed three half-marathons and founded and led two student organizations: 
GAIA (Global Action Impact Association) and SNAC (Student Neurodiversity Alliance at Cornell).
Becca graduated from MIT in 2021 with a B.S. in Mechanical Engineering. 
At MIT, she focused on electric vehicles, writing her bachelor's thesis on electric motor optimization for Formula SAE cars. 
\end{biosketch}

\begin{dedication}
This dissertation is dedicated to my neurokin:
all neurodivergent people across space, time, and context.
Thinking differently is a gift.
Let's make sure the world knows it.
\end{dedication}

\begin{acknowledgements}
\emph{The people you love will change you.
The things you have learned will guide you. 
And nothing on earth can silence the quiet voice still inside you.} 

- Moana

The PhD was hard in a way that undergrad wasn't.
The technical challenges were simple compared to the emotional, mental, and structural/systemic challenges.
I learned a lot about myself and what I need to be successful,
how to navigate inaccessible systems, how to advocate for myself and others, 
and how to both enact and know the limits of grassroots systemic change.
and got a lot of experience building, overhauling, 
and refining the processes and systems that help me navigate these challenges.
I am grateful to everyone who supported me through the process, including but not limited to:

First, I thank my academic and professional mentors and supporters, including:
\begin{itemize}
  \item Maha for taking me on as a student and ultimately persisting with me through the PhD process
  \item my committee members, Jacob, Pat, and Ryan, for their technical insight and feedback
  \item Sam and Dmitry, for stepping in to provide additional departmental advising support when I needed it 
  \item NREL for my undergraduate internship which exposed me to marine energy, includng my menor Scott Jenne
  \item Andras, my mentor at my internship at Infinite Cooling, 
  for showing me what someone with a PhD can do in industry and for being my role model
  \item Racecar (the MIT Formula SAE Team) for raising me as an engineer and giving me the technical skills 
  in multidisciplinary modeling and practical design and teamwork experience
  \item Physical and mental healthcare support and advising system, 
  including Rachel, Dawn, Erin, Ila, Matt
\end{itemize} 

Next, I thank my academic and extracurricular peers at Cornell:
\begin{itemize}
  \item SEA Lab for being a fun and supportive research group: 
  Can Jam on the fifth floor of Upson, PhD meetings, running, the hot tub
  \item Olivia V for being my best friend in the lab, conference buddy, 
  and for being there for each other when our phds were hard
  \item Nate, Matt, and Kapil, for making the lab fun with their antics. 
  One day we'll build a nuclear outer-space WEC.
  \item other MAE PhD students, including Colby, Charlotte, Diane, Jared. 
  The DnD campaign where Onaam Timunuo got to meet his grandfather, who talks to rocks.
  \item everyone who was willing to body double with me, including 
  Colby, Arthur, Joe, Demola, Stefan, Matt, Olivia V, Olivia G, Shariwa, Sam, Hana, and Jared.
  \item all the undergrads I've had the pleasure of mentoring, 
  including Madison who has worked with me for 4 years and has grown so much, 
  and En, Andrea, and Moho, who turned wait terrace into a SEA Lab house.
  Teamwork is really important to me, 
  \item Flor for being a devoted SNAC advisor; SNAC members 
  including Matthew, Anthony, Jessa, Will, Ethan, Sierra, Aishat
  \item the engineering leadership program, including professor Rob and Erica, 
  the geckos cohort, and the GAIA co-founders Mark and Moe.
  \item other GAIA members, including AJ, Nicholas, Sofia, Erick
\end{itemize}

Next, I thank my friends and housemates outside of the academic environment, including:
\begin{itemize}
  \item the CGSU graduate union for their energy to stand up to injustices 
  that are startlingly common in academia and beyond,
  and willingness to fight for me and my fellow graduate students
  \item Meghana for being the best friend I could ask for and always being a phone call away 
  for life debriefs, support, and even the times where 
  we just exist together mutually distracted on the phone.
  You have been my sounding board since the very beginning deciding where to go to grad school 
  and an invaluable friend throughout the process.
  Thanks for calling me out on my perfectionism, 
  helping me reflect on what I've learned about myself and what I want, 
  and for just getting me.
  You sometimes know me better than I know myself, 
  and I would be a different person without you.
  \item the wonderful housemates of Wait terrace cooperative 
  for late night wagon rides, floor time, squirrels in the walls, fridge quotes, karaoke
  \item Marina, Karen, and Marc, for cultivating a thriving house culture 
  full of Bob the Builder cakes, eight foot inflatable gnomes, and british accents.
  \item Ilana, Olivia G, and Firdavs, for being great co-house managers 
  and spending lovely midnights together on the Beebee Lake bridge. 
  I leave the house in your capable hands.
  \item Other roommates during PhD, including Andrea, Alexa, and Helena
  \item Ilana, my beloved roommate for the last 1.5 years, 
  who has been there for both the uncontrollable giggles and the uncontrollable tears.
  Yes, you can still be my roommate even if you turn into Kafka's beetle, 
  a pickled worm in a jar, or an inanimate object.
  Thanks for encouraging me to write Sun articles, 
  inviting me on that barefoot 4am walk to Goldwin Smith, 
  and helping me cement my identity.
  One day you'll be a PhD too, and maybe we'll start that questionable cult together (kidding).
  You're like a little sister to me, and I can't wait to see what's ahead for you.
\end{itemize}

Finally, I thank my family, including:
\begin{itemize}
  \item Brielle, who really is a little sister to me, 
  and sends me encouragement, hometown updates, handmade craft gifts, 
  and hidden little notes that always make me smile.
  \item My parents, for raising me to love learning enough to start a PhD 
  and to have the persistence to finish it.
  you keep a watchful eye on the Cornell red-tailed hawk cam, 
  and the annual excitement of the fledging of the hawks has marked the milestones of my PhD journey.
  I hope that with this thesis, I have likewise taken flight.
\end{itemize}


To everyone who has supported and encouraged me throughout this journey, thank you.
I love you all.

\end{acknowledgements}

\contentspage
\tablelistpage
\figurelistpage

\normalspacing \setcounter{page}{1} \pagenumbering{arabic}
\pagestyle{cornell} \addtolength{\parskip}{0.5\baselineskip}

\chapter{Introduction}\label{ch:intro}
\input{intro-contrib}

\chapter[System Modeling]{System Modeling\\
\large Development, Validation, and Benchmarking of a \\[-4ex]
Multidisciplinary Semi-Analytical Model for Wave Energy Converters}
\label{ch:modeling}

\emph{All models are wrong, but some are useful.}

- George Box, 1987

This chapter is adapted from \cite{mccabe_development_2026}, \hl{(pending submission)} [currently under review] for publication in Applied Ocean Research.
See \cref{sec:research-outputs} for other research outputs associated with this work.
\subimport{../applied-ocean-research-model/}{content}

\chapter[Hydrodynamic Modeling]{Hydrodynamic Modeling\\
\large Matrix Structure and Convergence Behavior of the\\[-4ex] 
Matched Eigenfunction Method for Generalized Concentric Bodies}
\label{ch:hydrodynamic}

\emph{The purpose of computing is insight, not numbers.}

- Richard Hamming, 1962

This chapter is adapted from \cite{bimali_matrix_2026}, currently under review for publication in the Journal of Fluid Mechanics (submission number JFM-2026-1453).
See \cref{sec:research-outputs} for other research outputs associated with this work.

\subimport{../../mdocean/simulation/modules/OpenFLASH/pubs/JFM/}{FLMguide}

\chapter[Design Optimization]{Design Optimization\\
\large Leveraging Multidisciplinary Design Optimization to \\[-4ex]
Advance Wave Energy Converter Viability
}
\label{ch:optimization}

\emph{The performance of a system doesn't depend on how the parts perform taken separately, it depends on how they perform together. [...] When you improve the performance of a part of a system taken separately, you can destroy the system.}

- Russell Ackoff, 2003 \cite{ackoff_video_2003}

This chapter is adapted from \cite{mccabe_leveraging_2026}, \hl{(pending submission)} [currently under review] for publication in Renewable Energy.
See \cref{sec:research-outputs} for other research outputs associated with this work.
\subimport{../renewable-energy-mdo/}{content-re}

\chapter[Grid Impact Synthesis]{Grid Impact Synthesis\\
\large
A Paradigm for Grid-Informed Design Optimization\\[-4ex] 
to Maximize System Economic and Environmental Value}
\label{ch:grid-value}

\emph{We should no longer measure our wealth and success in the graph that shows economic growth, but in the curve that shows the emissions of greenhouse gases.}

- Greta Thunberg, 2019 \cite{thunberg_speech_2019}

This chapter is currently unpublished.
See \cref{sec:research-outputs} for research outputs associated with this work.
\subimport{../UMERC-2025-grid-value/}{content-grid}

\chapter{Conclusion}
\hl{A conclusion will be written here}.
% \chapter{Vision for the Future of Wave Energy Optimization}
% - extend to other architectures and more complex models (already written in modeling paper)
% - integrate with wecopttool and wecsim

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\begin{appendices}

\chapter{System Modeling Appendices}
\subimport{../applied-ocean-research-model/}{appendices}

\chapter{Hydrodynamic Modeling Appendices}
\subimport{../../mdocean/simulation/modules/OpenFLASH/pubs/JFM/}{jfm-appendix}

\chapter{Design Optimization Appendices}
\subimport{../renewable-energy-mdo/sections/}{other-appendices}

\chapter{Grid Impact Synthesis Appendices}
\section{Reduced order model details}
\subimport{../UMERC-2025-grid-value/}{appendix-grid}

\end{appendices}

\addcontentsline{toc}{chapter}{\bibname}
\bibliography{references,jfm,zotero-meem-refs}

\end{document}
