\input{sections/model-intro}
%\clearpage
\input{sections/model-overview}
%\clearpage
\input{sections/module-details}
%\clearpage
\input{sections/benchmarking}
%\clearpage
\input{sections/discussion}

\section{Conclusion}
% Summary:
This paper develops MDOcean, an open-source semi-analytical modeling framework for two-body axisymmetric point-absorber wave energy converters that integrates hydrodynamics, dynamics, control, structures, and economics in a single fast simulation.

% Model
\ifdefined\DISSERTATION
    The geometry module calculates volumes, areas, and the pitch stability margin with simple algebraic relations, and the economics module calculates design-dependent cost from structural material volume and powertrain force and power ratings.
    The hydrodynamics module implements the matched eigenfunction expansion method (MEEM) for a dual concentric cylinder geometry to obtain the float radiation coefficients, and interpolates existing BEM solutions to obtain the spar radiation coefficients due to the lack of a damping plate in the current MEEM model.
    This achieves an order of magnitude speedup compared to the popular BEM solver Capytaine.
    The dynamics module employs describing functions to extend the typical frequency-domain formulation to capture nonlinearities and dynamic constraints, including viscous drag and generator force saturation, and includes a novel analytical quadratically-constrained quadratic program (QCQP) for the constrained linear controller.
    This achieves a three-order-of-magnitude computational speedup over the common time-domain solver WEC-Sim.
    The structures module uses an equivalent-thickness model of stiffened plates and a library of canonical solutions to structural boundary-value problems to assess the factor of safety of the float bottom plate, spar shell, and damping plate in cyclic fatigue and storm load cases.
    This represents, to the authors' knowledge, the only public WEC structural simulation regardless of modeling technique.
    Finally, the economics module calculates the design-dependent cost based on structural material volume and powertrain force and power rating, performing a straightforward LCOE calculation.
\else
    The geometry module handles hydrostatics.
    The hydrodynamics module uses the matched eigenfunction expansion method (MEEM) for the float, achieving an order-of-magnitude speedup over BEM.
    The dynamics module employs describing functions and a novel analytical QCQP for constrained linear control, achieving a three-order-of-magnitude speedup over time-domain solvers.
    The structures module uses semi-analytical stiffened-plate models with realistic failure criteria for fatigue and storm load cases---to the authors' knowledge, the only public WEC structural simulation.
    The economics module includes a calibrated cost model.
    Full MEEM derivation appears in the forthcoming \cite{bimali_matrix_2026}.
\fi


Validation against WEC-Sim and the RM3 reference design demonstrates that MDOcean reproduces the dynamics of an established time-domain solver to within a few percent under matched modeling assumptions and within single-digit-percent JPD-weighted annual average power under realistic conditions, despite worst-case per-sea-state errors that can be larger due to drag and inter-body phase sensitivity in the 2-DOF model.
Three tuned scale factors, on storm force, average power, and structural mass, bring the simulated outputs within 1\% of the reference model report across all major modules.
Total simulation runtime is \resultsAOR[simRuntime], which is 1-3 orders of magnitude faster than established baselines and enables multidisciplinary optimization workflows that would otherwise be prohibitive.

The methodological contribution most relevant to the broader WEC modeling community is the modified frequency-domain dynamics formulation, which unifies prior describing-function and constrained-control approaches and adds a closed-form QCQP solution with a geometric interpretation on the complex plane of the reflection coefficient.
This solves analytically a problem that previously required numerical optimization, and we believe it is the first application of describing functions for both controller synthesis and evaluation in wave energy.

More broadly, the results suggest that semi-analytical multidisciplinary modeling can provide a useful intermediate between simplified conceptual studies and computationally intensive high-fidelity simulation, enabling both rapid optimization and improved physical insight during early-stage WEC development.

% Discussion
\ifdefined\DISSERTATION
    A key feature of this study that other WEC models lack is the inclusion of more realistic effects such as shape-informed structural stress, force saturation, amplitude limits, and a nonlinear drag model.
    Nonetheless, the model has limitations: the structural loads and stresses have non-trivial uncertainty due to the regular-wave assumption in storm load cases; the impact of irregular waves on operational power and constraints is approximated rather than directly modeled; surge force is not propagated to the structures module and no mooring cost model is included; and only a single WEC archetype (two-body axisymmetric point absorber) is considered.
    Future modeling work should pursue these enhancements alongside extensions to additional WEC archetypes, generator magnetics, and probabilistic / spectral analyses for fatigue, grid integration, and storage sizing.
\else
    Principal limitations include the regular-wave assumption in storm load cases, the approximation of irregular-wave operational dynamics through equivalent regular waves, the absence of surge force in the structures module and of a mooring cost model, and restriction to a single WEC archetype.
Detailed future-work directions are given in \cref{sec:unmodeled-effects}.
\fi

% Impact of findings:
The companion paper \cite{mccabe_leveraging_2026} applies MDOcean to a multidisciplinary techno-economic optimization of the RM3 reference design.
MDOcean is open-source and is intended to support continued community development of fast multidisciplinary WEC modeling tools that integrate insights from hydrodynamics, controls, structures, and economics in a unified framework.